Incentivizing Exploration with Unbiased History

### 2018-10-29 llevel.tex
llevel

\section{Missing Proofs of Section \ref{sec:llevel}}
\label{sec:llevel-details}
In this section, we design an $L$-level recommendation policy for $L > 3$ and 2 arms. By having more than 3 levels, we get even smaller regret.

Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups. Each level has $S^2$ $G$-groups for $S = 2^{10}\log(T)$. Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [S]$. Level $2$ to level $L$ also have $S^2$ $\Gamma$-groups. Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$. Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel. For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$. We will pick $T_1,...,T_L$ in the proof of Theorem \ref{thm:llevel}.

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=orange!20!white]
 (\x+0,10)--(\x+0.8,10)--(\x+0.8,11)--(\x+0,11)--cycle;
 \filldraw[fill=orange!30!white]
 (\x+0.8,10)--(\x+2.8,10)--(\x+2.8,11)--(\x+0.8,11)--cycle;
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+0.8,7.5)--(\x+0.8,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=purple!30!white]
 (\x+0.8,7.5)--(\x+2.8,7.5)--(\x+2.8,8.5)--(\x+0.8,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+0.8,5)--(\x+0.8,6)--(\x+0,6)--cycle;
 \filldraw[fill=green!30!white]
 (\x+0.8,5)--(\x+2.8,5)--(\x+2.8,6)--(\x+0.8,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+0.8,2.5)--(\x+0.8,3.5)--(\x+0,3.5)--cycle;
 \filldraw[fill=blue!30!white]
 (\x+0.8,2.5)--(\x+2.8,2.5)--(\x+2.8,3.5)--(\x+0.8,3.5)--cycle;
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2.8,0)--(\x+2.8,1)--(\x+0,1)--cycle;
 \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
 \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
 \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
 \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
 \draw[dashed] (\x+2,0)--(\x+2,1);  
 \draw[dashed] (\x+2.4,0)--(\x+2.4,1);  
 \node at(\x+0.4,3){$T_{l-2}$};
 \node at(\x+1.8,3){$T_{l-2} (S-1)$};
 \node at(\x+0.4,5.5){$T_{l-1}$};
 \node at(\x+1.8,5.5){$T_{l-1} (S-1)$};
 \node at(\x+0.4,8){$T_l$};
 \node at(\x+1.8,8){$T_l (S-1)$};
 \node at(\x+0.4,10.5){$T_L$};
 \node at(\x+1.8,10.5){$T_L (S-1)$};
 \node at(\x+1.4,0.5){$T_1 \cdot \GdT$};
 }
\foreach \y in {0,2.5,5,7.5,10}
{
  \node at (12.5,\y+0.5){$\cdots$};
} 
\foreach \u in {1,2}
{
	\foreach \v in {1,2}
	{
	\pgfmathsetmacro{\x}{((\u-1)*2+(\v-1))*3};
	\pgfmathsetmacro{\xa}{((\u-1))*3};
	\pgfmathsetmacro{\xb}{(2+(\u-1))*3};
   \node at(\x+0.6,7){$G_{l,\u,\v}$};
   \node at(\x+0.6,4.5){$G_{l-1,\u,\v}$};
   \node at(\x+0.6,2){$G_{l-2,\u,\v}$};
   \node at(\x+2,7){$\Gamma_{l,\u,\v}$};
   \node at(\x+2,4.5){$\Gamma_{l-1,\u,\v}$};
   \node at(\x+2,2){$\Gamma_{l-2,\u,\v}$};
   %\draw[dashed] (\x+0.4,3.5)--(\xa+0.4,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xb+0.4,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xa+1.8,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xb+1.8,5);

@@

   \draw[dashed] (0+0.4,6)--(6.4,7.5);  	
   \draw[dashed] (3+0.4,6)--(6.4,7.5);  	
  \node at (6,1.5)[rotate = 90]{$\cdots$};
  \node at (-1,1.5)[rotate = 90]{$\cdots$};
  \node at (6,9.5)[rotate = 90]{$\cdots$};
  \node at (-1,9.5)[rotate = 90]{$\cdots$};
  \node at(-1.2,0.5){\textbf{Level 1}};
  \node at(-1.2,3){\textbf{Level $l-2$}};
  \node at(-1.2,5.5){\textbf{Level $l-1$}};
  \node at(-1.2,8){\textbf{Level $l$}};
  \node at(-1.2,10.5){\textbf{Level $L$}};
  \draw[->] (13.3,0)--(13.3,12);
  \node at(13.7,6)[ rotate=90]{Time};
  \draw [rounded corners=5mm, line width=1mm, red](-0.2,1.75)--(12,1.75)--(12,9)--(-0.2,9)--cycle;\draw [rounded corners=2.5mm, line width=0.5mm, brown](5.9,6.5)--(8.9,6.5)--(8.9,8.8)--(5.9,8.8)--cycle;
\end{tikzpicture}
\caption{$l$-level Recommendation Policy.}
\label{fig:llevel}
\end{figure}

>>>>

\section{Missing Proofs of Section \ref{sec:llevel}}
\label{sec:llevel-details}
In this section, we design our $L$-level recommendation policy for $L > 3$. Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}). We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).

Now we start with the case of 2 arms. Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups. Each level has $S^2$ $G$-groups for $S = 2^{10}\log(T)$. Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [S]$. Level $2$ to level $L$ also have $S^2$ $\Gamma$-groups. Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$. Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel. For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$. We will pick $T_1,...,T_L$ in the proof of Theorem \ref{thm:llevel}.

@@

 \begin{comment}
\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=orange!20!white]
 (\x+0,10)--(\x+0.8,10)--(\x+0.8,11)--(\x+0,11)--cycle;
 \filldraw[fill=orange!30!white]
 (\x+0.8,10)--(\x+2.8,10)--(\x+2.8,11)--(\x+0.8,11)--cycle;
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+0.8,7.5)--(\x+0.8,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=purple!30!white]
 (\x+0.8,7.5)--(\x+2.8,7.5)--(\x+2.8,8.5)--(\x+0.8,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+0.8,5)--(\x+0.8,6)--(\x+0,6)--cycle;
 \filldraw[fill=green!30!white]
 (\x+0.8,5)--(\x+2.8,5)--(\x+2.8,6)--(\x+0.8,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+0.8,2.5)--(\x+0.8,3.5)--(\x+0,3.5)--cycle;
 \filldraw[fill=blue!30!white]
 (\x+0.8,2.5)--(\x+2.8,2.5)--(\x+2.8,3.5)--(\x+0.8,3.5)--cycle;
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2.8,0)--(\x+2.8,1)--(\x+0,1)--cycle;
 \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
 \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
 \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
 \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
 \draw[dashed] (\x+2,0)--(\x+2,1);  
 \draw[dashed] (\x+2.4,0)--(\x+2.4,1);  
 \node at(\x+0.4,3){$T_{l-2}$};
 \node at(\x+1.8,3){$T_{l-2} (S-1)$};
 \node at(\x+0.4,5.5){$T_{l-1}$};
 \node at(\x+1.8,5.5){$T_{l-1} (S-1)$};
 \node at(\x+0.4,8){$T_l$};
 \node at(\x+1.8,8){$T_l (S-1)$};
 \node at(\x+0.4,10.5){$T_L$};
 \node at(\x+1.8,10.5){$T_L (S-1)$};
 \node at(\x+1.4,0.5){$T_1 \cdot \GdT$};
 }
\foreach \y in {0,2.5,5,7.5,10}
{
  \node at (12.5,\y+0.5){$\cdots$};
} 
\foreach \u in {1,2}
{
	\foreach \v in {1,2}
	{
	\pgfmathsetmacro{\x}{((\u-1)*2+(\v-1))*3};
	\pgfmathsetmacro{\xa}{((\u-1))*3};
	\pgfmathsetmacro{\xb}{(2+(\u-1))*3};
   \node at(\x+0.6,7){$G_{l,\u,\v}$};
   \node at(\x+0.6,4.5){$G_{l-1,\u,\v}$};
   \node at(\x+0.6,2){$G_{l-2,\u,\v}$};
   \node at(\x+2,7){$\Gamma_{l,\u,\v}$};
   \node at(\x+2,4.5){$\Gamma_{l-1,\u,\v}$};
   \node at(\x+2,2){$\Gamma_{l-2,\u,\v}$};
   %\draw[dashed] (\x+0.4,3.5)--(\xa+0.4,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xb+0.4,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xa+1.8,5);  
   %\draw[dashed] (\x+0.4,3.5)--(\xb+1.8,5);

@@

   \draw[dashed] (0+0.4,6)--(6.4,7.5);  	
   \draw[dashed] (3+0.4,6)--(6.4,7.5);  	
  \node at (6,1.5)[rotate = 90]{$\cdots$};
  \node at (-1,1.5)[rotate = 90]{$\cdots$};
  \node at (6,9.5)[rotate = 90]{$\cdots$};
  \node at (-1,9.5)[rotate = 90]{$\cdots$};
  \node at(-1.2,0.5){\textbf{Level 1}};
  \node at(-1.2,3){\textbf{Level $l-2$}};
  \node at(-1.2,5.5){\textbf{Level $l-1$}};
  \node at(-1.2,8){\textbf{Level $l$}};
  \node at(-1.2,10.5){\textbf{Level $L$}};
  \draw[->] (13.3,0)--(13.3,12);
  \node at(13.7,6)[ rotate=90]{Time};
  \draw [rounded corners=5mm, line width=1mm, red](-0.2,1.75)--(12,1.75)--(12,9)--(-0.2,9)--cycle;\draw [rounded corners=2.5mm, line width=0.5mm, brown](5.9,6.5)--(8.9,6.5)--(8.9,8.8)--(5.9,8.8)--cycle;
\end{tikzpicture}
\caption{$l$-level Recommendation Policy.}
\label{fig:llevel}
\end{figure}
\end{comment}
